---
title: "Attitudes toward equality - part 1"
author: "Pamela Inostroza Fernández"
date: "November 2020"
output: 
  html_document:
    keep_md: true
    toc: TRUE
    toc_depth: 1
    toc_float: 
      collapsed: true
    number_sections: true
    theme: united
    highlight: tango
editor_options: 
  chunk_output_type: console
---

# Files analyzed  

The present document has the finality of summarize some of the analysis that can be done using CIVED/ICCS data set to study the scales regarding Attitudes toward diverse social groups, such as **Attitudes toward equal rights for all ethnic/racial groups**, **Attitudes toward gender equality** and **Attitudes toward equal rights for immigrants**. Three cycles are available and multiple countries participate in each one of them.

This summary include the following selected countries and years (cycle) in the analysis.  

```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
#knitr::opts_knit$set(root.dir = 'C:/Users/pamel/OneDrive - KU Leuven/Master in Statistics/Master Thesis')
library(haven)
library(readxl)
library(tidyverse)
options(scipen = 999)
options(knitr.kable.NA = '')

#setwd("C:/Users/pamel/OneDrive - KU Leuven/Master in Statistics/Master Thesis/")
```  

**Participant countries**  

The participant countries were divided in 5 groups:  

a. Nordic Countries: Denmark, Finland, Norway, Sweden.  
b. Western European Countries: Belgium (Flemish), The Netherlands.  
c. Central and Eastern European Countries: Bulgaria, Estonia, Latvia, Lithuania, Croatia, Slovenia.  
d. Southern European Countries: Italy, Malta.  
e. Latin American Countries: Chile, Peru, Colombia, Dominican Republic, Mexico.  

```{r data}
Countries <- read_xlsx("Metadata.xlsx", sheet = "CNT")
Files <- read_xlsx("Metadata.xlsx", sheet = "Files")
CNTa <- c("DNK", "FIN", "NOR", "SWE")
CNTb <- c("BFL", "NLD")
CNTc <- c("BGR", "EST", "LVA", "LTU", "HRV", "SVN")
CNTd <- c("ITA", "MLT")
CNTe <- c("CHL", "PER", "COL", "DOM", "MEX")
CNT <- c(CNTa, CNTb, CNTc, CNTd, CNTe)
# c(AUS", "BFL", "BGR", "CHE", "CHL", "COL", "CYP", "CZE", "DEU", "DNK", "DOM", "ENG", "ESP", "EST", "FIN", "FRA", "GRC", "HKG", "HRV", "HUN", "ISR", "ITA", "KOR", "LTU", "LVA", "MEX", "MLT", "NLD", "NOR", "PER", "POL", "PRT", "ROM", "RUS", "SRB", "SVK", "SVN", "SWE", "TWN", "USA") CNTb #

Itemdesc <- read_xlsx("Items scales.xlsx", sheet = "Scales")
years <- Countries %>% filter(AlphaCode %in% CNT & !is.na(Part)) %>% dplyr::select(Country, AlphaCode, year) 

```

```{r namesfiles, comment="", eval=FALSE}
filenames <- NULL
cat("Countries selected and year participation in CIVED/ICCS:  \n")

for (cnt in CNT) {

  yearf <- years %>% filter(AlphaCode == cnt & year != 22) %>% arrange(as.numeric(year))
  
  cat(paste0(unique(yearf$Country), " : ", paste(sort(ifelse(yearf$year == "99", paste0("19",yearf$year), paste0("20",yearf$year))), collapse = " ")),'  \n')

  for (yearn in yearf$year) {
 
    CountryEU <- Countries %>% filter(year == yearn & !is.na(EUQ)) %>% dplyr::select(AlphaCode)
    CountryLA <- Countries %>% filter(year == yearn & !is.na(LAQ)) %>% dplyr::select(AlphaCode) 
    Teacher <- Countries %>% filter(year == yearn & !is.na(ITG)) %>% dplyr::select(AlphaCode) 
    School <- Countries %>% filter(year == yearn & !is.na(ICG)) %>% dplyr::select(AlphaCode) 
    
    if (yearn == "99") Folder <- paste0("CivED19",yearn,"_IDB_SPSS_G8") else
      Folder <- paste0("ICCS20",yearn,"_IDB_SPSS")
    File <- Files %>% filter(!is.na(ToUse)) %>% dplyr::select(Filename)
    if (yearn == "99") cycle = "f2" else if (yearn == "09") cycle = "C2" else if (yearn == "16") cycle = "C3" else 
      if (yearn == "22") cycle = "C4"
    if (yearn == "99") {
      filenames <- c(filenames, paste0(Folder, "/Data/", "bs_", tolower(cnt), cycle,".sav"))
      if (cnt %in% Teacher$AlphaCode) filenames <- c(filenames, paste0(Folder, "/Data/", "bt_", tolower(cnt), cycle,".sav"))
      if (cnt %in% School$AlphaCode) filenames <- c(filenames, paste0(Folder, "/Data/", "bc_", tolower(cnt), cycle,".sav"))
    } else {
      if (cnt %in% CountryLA$AlphaCode) filenames <- c(filenames, paste0(Folder, "/Data/", "ISL",cnt,cycle,".sav"))
      if (cnt %in% CountryEU$AlphaCode) filenames <- c(filenames, paste0(Folder, "/Data/", "ISE",cnt,cycle,".sav")) 
      filenames <- c(filenames, paste0(Folder, "/Data/", "ISG",cnt,cycle,".sav"))
      if (cnt %in% Teacher$AlphaCode) filenames <- c(filenames, paste0(Folder, "/Data/", "ITG",cnt,cycle,".sav"))
      if (cnt %in% School$AlphaCode) filenames <- c(filenames, paste0(Folder, "/Data/", "ICG",cnt,cycle,".sav")) 
    }
  }
}
#order by questionnaire and cycle
filenames <- filenames[order(substr(filenames,24,26),substr(filenames,30,31))] 
rm(list = c("yearf", "cnt", "cycle", "Folder", "yearn", "File", "CountryEU", "CountryLA"))
```

```{r read_spss, eval=FALSE}
ICGC1 <- NULL
ICGC2 <- NULL
ICGC3 <- NULL
ITGC1 <- NULL
ITGC2 <- NULL
ITGC3 <- NULL
ISGC1 <- NULL
ISGC2 <- NULL
ISGC3 <- NULL
ISEC2 <- NULL
ISEC3 <- NULL
ISLC2 <- NULL
ISLC3 <- NULL

for (nc in 1:length(filenames)) {
  print(paste("nc:",filenames[nc]))
  if (substr(filenames[nc],24,26) == "ICG" | substr(filenames[nc],28,30) == "bc_") {
    if (substr(filenames[nc],34,35) == "f2") {
      dataset <- read_sav(file.path("Data", filenames[nc]))
      dataset_r <- dataset %>% rename_at(vars(colnames(dataset)), ~ toupper(colnames(dataset)))
      ICGC1 <- rbind(ICGC1, dataset_r)
    } else if (substr(filenames[nc],30,31) == "C2") {
      dataset <- read_sav(file.path("Data", filenames[nc]))
      ICGC2 <- rbind(ICGC2, dataset)
    } else if (substr(filenames[nc],30,31) == "C3") {
      dataset <- read_sav(file.path("Data", filenames[nc]))
      ICGC3 <- rbind(ICGC3, dataset)
    }
  }
  if (substr(filenames[nc],24,26) == "ITG" | substr(filenames[nc],28,30) == "bt_"){
    if (substr(filenames[nc],34,35) == "f2") {
      dataset <- read_sav(file.path("Data", filenames[nc]))
      dataset_r <- dataset %>% rename_at(vars(colnames(dataset)), ~ toupper(colnames(dataset)))
      ITGC1 <- rbind(ITGC1, dataset_r)
    } else if (substr(filenames[nc],30,31) == "C2") {
      dataset <- read_sav(file.path("Data", filenames[nc]))
      ITGC2 <- rbind(ITGC2, dataset)
    } else if (substr(filenames[nc],30,31) == "C3") {
      dataset <- read_sav(file.path("Data", filenames[nc]))
      ITGC3 <- rbind(ITGC3, dataset)
    }
  }
  
  if (substr(filenames[nc],24,26) == "ISG" | substr(filenames[nc],28,30) == "bs_"){
   if (substr(filenames[nc],34,35) == "f2") {
      dataset <- read_sav(file.path("Data", filenames[nc]))
      dataset_r <- dataset %>% rename_at(vars(colnames(dataset)), ~ toupper(colnames(dataset)))
      dataset_r$IMMIGMLE <- labelled(dataset_r$IMMIGMLE, labels =  c(INVALID = 97, OMITTED = 99), label = attr(dataset_r$IMMIGMLE, "label"))
      dataset_r$WOMRTMLE <- labelled(dataset_r$WOMRTMLE, labels =  c(INVALID = 97, OMITTED = 99), label = attr(dataset_r$WOMRTMLE, "label"))
      ISGC1 <- rbind(ISGC1, dataset_r)
    } else if (substr(filenames[nc],30,31) == "C2") {
      dataset <- read_sav(file.path("Data", filenames[nc]))
      ISGC2 <- rbind(ISGC2, dataset)
    } else if (substr(filenames[nc],30,31) == "C3") {
      dataset <- read_sav(file.path("Data", filenames[nc]))  
      ISGC3 <- rbind(ISGC3, dataset)
    }
  }
  
  if (substr(filenames[nc],24,26) == "ISE") {
    if (substr(filenames[nc],30,31) == "C2") {
      dataset <- read_sav(file.path("Data", filenames[nc]))
      ISEC2 <- rbind(ISEC2, dataset)
    } else if (substr(filenames[nc],30,31) == "C3") {
      dataset <- read_sav(file.path("Data", filenames[nc]))  
      ISEC3 <- rbind(ISEC3, dataset)
    }
  }
  if (substr(filenames[nc],24,26) == "ISL") {
    if (substr(filenames[nc],30,31) == "C2") {
      dataset <- read_sav(file.path("Data", filenames[nc]))
      ISLC2 <- rbind(ISLC2, dataset)
    } else if (substr(filenames[nc],30,31) == "C3") {
      dataset <- read_sav(file.path("Data", filenames[nc]))  
      ISLC3 <- rbind(ISLC3, dataset)
    }
  }
}
ISGC1$cycle <- "C1"
ISGC2$cycle <- "C2"
ISGC3$cycle <- "C3"
ISEC2$cycle <- "C2"
ISEC3$cycle <- "C3"
ISLC2$cycle <- "C2"
ISLC3$cycle <- "C3"

ITGC1$cycle <- "C1"
ITGC2$cycle <- "C2"
ITGC3$cycle <- "C3"
ICGC1$cycle <- "C1"
ICGC2$cycle <- "C2"
ICGC3$cycle <- "C3"

ISGC1$questG <- "ISG"
ISGC2$questG <- "ISG"
ISGC3$questG <- "ISG"
ISEC2$questE <- "ISE"
ISEC3$questE <- "ISE"
ISLC2$questL <- "ISL"
ISLC3$questL <- "ISL"

ITGC1$questT <- "ITG"
ITGC2$questT <- "ITG"
ITGC3$questT <- "ITG"
ICGC1$questC <- "ICG"
ICGC2$questC <- "ICG"
ICGC3$questC <- "ICG"

ISGC1 <- ISGC1 %>% rename_at(vars(c("TOTWGT","SENWGT", "JKZONE")), ~ c("TOTWGT_Gc1", "SENWGT_Gc1", "JKZONES"))
ISGC2 <- ISGC2 %>% rename_at(vars(c("TOTWGTS","SENWGTS", "HOMELIT")), ~ c("TOTWGT_Gc2", "SENWGT_Gc2","SHOMELIT"))
ISGC3 <- ISGC3 %>% rename_at(vars(c("TOTWGTS")), ~ c("TOTWGT_Gc3"))

ISEC2 <- ISEC2 %>% rename_at(vars(c("TOTWGTS","SENWGTS")), ~ c("TOTWGT_Ec2", "SENWGT_Ec2"))
ISEC3 <- ISEC3 %>% rename_at(vars(c("TOTWGTS")), ~ c("TOTWGT_Ec3"))
ISLC2 <- ISLC2 %>% rename_at(vars(c("TOTWGTS","SENWGTS")), ~ c("TOTWGT_Lc2", "SENWGT_Lc2"))
ISLC3 <- ISLC3 %>% rename_at(vars(c("TOTWGTS")), ~ c("TOTWGT_Lc3"))

#ITGC1 <- ITGC1 %>% rename_at(vars(c()), ~ c("TOTWGT_Tc1", "SENWGT_Tc1"))
ITGC2 <- ITGC2 %>% rename_at(vars(c("TOTWGTT","SENWGTT")), ~ c("TOTWGT_Tc2", "SENWGT_Tc2"))
ITGC3 <- ITGC3 %>% rename_at(vars(c("TOTWGTT")), ~ c("TOTWGT_Tc3"))

ICGC1 <- ICGC1 %>% rename_at(vars(c("SCHWGT","STDWGT")), ~ c("TOTWGT_Cc1", "SENWGT_Cc1"))
ICGC2 <- ICGC2 %>% rename_at(vars(c("TOTWGTC")), ~ c("TOTWGT_Cc2"))
ICGC3 <- ICGC3 %>% rename_at(vars(c("TOTWGTC")), ~ c("TOTWGT_Cc3"))

#rm(list = c("dataset","nc","filenames"))

#---------------------------------------------
#---------------------------------------------
#---------------------------------------------
#------Summary sample Cycle 1 ----------------
#------Student general questionnaire ---------

ISGC1 %>% dplyr::select(TOTWGT_Gc1,SENWGT_Gc1, JKZONES, COUNTRY, IDSCHOOL, cycle, questG) %>% 
  group_by(COUNTRY, cycle, questG) %>% 
  summarise(W99 = sum(TOTWGT_Gc1, na.rm = TRUE),
            WS99 = round(sum(SENWGT_Gc1, na.rm = TRUE),0),
            nStr99 = n_distinct(JKZONES),
            nSch99 = n_distinct(IDSCHOOL),
            nStu99 = n()) %>% knitr::kable()

#------Stratum with only one school------------
ISGC1 %>% dplyr::select(JKZONES, COUNTRY, IDSCHOOL, cycle, questG) %>% group_by(COUNTRY, cycle, questG, JKZONES) %>% 
  summarise(n_schools = n_distinct(IDSCHOOL)) %>% group_by(cycle, COUNTRY, n_schools) %>% count() %>% filter(n_schools == 1)

#------Teacher general questionnaire ---------
# ITGC1 <- ITGC1 %>%  group_by(COUNTRY, cycle, questT) %>%
#   mutate(SENWGT_Tc1 = (TOTWGT_Tc1/sum(TOTWGT_Tc1))*1000) %>% ungroup()
# ITGC1 %>% dplyr::select(TOTWGT_Tc1,SENWGT_Tc1, COUNTRY, cycle, questT) %>%
#   group_by(COUNTRY, cycle, questT) %>%
#   summarise(w99 = round(sum(TOTWGT_Tc1, na.rm = TRUE),2),
#             WS99 = round(sum(SENWGT_Tc1, na.rm = TRUE),0),
#             n = n()) %>% knitr::kable()

#------School general questionnaire ---------
ICGC1 <- ICGC1 %>%  group_by(COUNTRY, cycle, questC) %>% 
  mutate(SENWGT_Cc1 = (TOTWGT_Cc1/sum(TOTWGT_Cc1))*1000) %>% ungroup()
ICGC1 %>% dplyr::select(TOTWGT_Cc1,SENWGT_Cc1, COUNTRY, cycle, questC) %>%
   group_by(COUNTRY, cycle, questC) %>% 
  summarise(w99 = round(sum(TOTWGT_Cc1, na.rm = TRUE),2),
            WS99 = round(sum(SENWGT_Cc1, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()


#---------------------------------------------
#------Summary sample Cycle 2 ----------------
#------Student general questionnaire ---------
ISGC2 <- ISGC2 %>% group_by(COUNTRY, cycle, questG) %>%
  mutate(SENWGT_Gc2 = (TOTWGT_Gc2/sum(TOTWGT_Gc2))*1000) %>% ungroup()
ISGC2 %>% dplyr::select(TOTWGT_Gc2, SENWGT_Gc2, JKZONES, COUNTRY, IDSCHOOL, cycle, questG)  %>% 
  group_by(COUNTRY, cycle, questG) %>% 
  summarise(W09 = sum(TOTWGT_Gc2, na.rm = TRUE),
            WS09 =sum(SENWGT_Gc2, na.rm = TRUE),
            nStr09 = n_distinct(JKZONES),
            nSch09 = n_distinct(IDSCHOOL),
            nStu09 = n()) %>% knitr::kable()

#------Student European questionnaire ---------
ISEC2 <- ISEC2 %>% group_by(COUNTRY, cycle, questE) %>% 
  mutate(SENWGT_Ec2 = (TOTWGT_Ec2/sum(TOTWGT_Ec2))*1000) %>% ungroup()
ISEC2 %>% dplyr::select(TOTWGT_Ec2,SENWGT_Ec2, JKZONES,COUNTRY, cycle, questE) %>% 
  group_by(COUNTRY, cycle, questE) %>% 
  summarise(W09 = round(sum(TOTWGT_Ec2, na.rm = TRUE),2),
            WS09 = round(sum(SENWGT_Ec2, na.rm = TRUE),0),
            nStr09 = n_distinct(JKZONES),
            nSch09 = n_distinct(IDSCHOOL),
            nStu09 = n()) %>% knitr::kable()

#------Student Latinam questionnaire ---------
ISLC2 <- ISLC2 %>% group_by(COUNTRY, cycle, questL) %>% 
  mutate(SENWGT_Lc2 = (TOTWGT_Lc2/sum(TOTWGT_Lc2))*1000) %>% ungroup()
ISLC2 %>% dplyr::select(TOTWGT_Lc2,SENWGT_Lc2, JKZONES, COUNTRY, cycle, questL) %>%
  group_by(COUNTRY, cycle, questL) %>%
  summarise(W09 = round(sum(TOTWGT_Lc2, na.rm = TRUE),2),
            WS09 = round(sum(SENWGT_Lc2, na.rm = TRUE),0),
            nStr09 = n_distinct(JKZONES),
            nSch09 = n_distinct(IDSCHOOL),
            nStu09 = n()) %>% knitr::kable()

#------Stratus with only one school------------
ISGC2 %>% dplyr::select(JKZONES, COUNTRY, IDSCHOOL, cycle, questG) %>% group_by(COUNTRY, cycle, questG, JKZONES) %>% 
  summarise(n_schools = n_distinct(IDSCHOOL)) %>% group_by(cycle, COUNTRY, n_schools) %>% count() %>% filter(n_schools == 1)

#------Teacher general questionnaire ---------
ITGC2 <- ITGC2 %>%  group_by(COUNTRY, cycle, questT) %>% 
  mutate(SENWGT_Tc2 = (TOTWGT_Tc2/sum(TOTWGT_Tc2))*1000) %>% ungroup()
ITGC2 %>% dplyr::select(TOTWGT_Tc2,SENWGT_Tc2, COUNTRY, cycle, questT) %>%
  group_by(COUNTRY, cycle, questT) %>% 
  summarise(w09 = round(sum(TOTWGT_Tc2, na.rm = TRUE),2),
            WS09 = round(sum(SENWGT_Tc2, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()

#------School general questionnaire ---------
ICGC2 <- ICGC2 %>% group_by(COUNTRY, cycle, questC) %>% 
  mutate(SENWGT_Cc2 = (TOTWGT_Cc2/sum(TOTWGT_Cc2))*1000) %>% ungroup()
ICGC2 %>% dplyr::select(TOTWGT_Cc2, SENWGT_Cc2, COUNTRY, cycle, questC) %>% 
  group_by(COUNTRY, cycle, questC) %>% 
  summarise(w09 = round(sum(TOTWGT_Cc2, na.rm = TRUE),2),
            WS09 = round(sum(SENWGT_Cc2, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()


#---------------------------------------------
#------Summary sample Cycle 3 ----------------
#------Student general questionnaire ---------
ISGC3 <- ISGC3 %>% group_by(COUNTRY, cycle, questG) %>% 
  mutate(SENWGT_Gc3 = (TOTWGT_Gc3/sum(TOTWGT_Gc3))*1000) %>% ungroup()
ISGC3 %>% dplyr::select(TOTWGT_Gc3, SENWGT_Gc3, JKZONES, COUNTRY, IDSCHOOL, cycle, questG) %>% 
  group_by(COUNTRY, cycle, questG) %>% 
  summarise(W16 = sum(TOTWGT_Gc3, na.rm = TRUE),
            WS16 = sum(SENWGT_Gc3, na.rm = TRUE),
            nStr16 = n_distinct(JKZONES),
            nSch16 = n_distinct(IDSCHOOL),
            nStu16 = n()) %>% knitr::kable()

#------Student European questionnaire ---------
ISEC3 <- ISEC3 %>% group_by(COUNTRY, cycle, questE) %>% 
  mutate(SENWGT_Ec3 = (TOTWGT_Ec3/sum(TOTWGT_Ec3))*1000) %>% ungroup()
ISEC3 %>% dplyr::select(TOTWGT_Ec3, SENWGT_Ec3, JKZONES, COUNTRY, cycle, questE) %>% 
  group_by(COUNTRY, cycle, questE) %>% 
  summarise(W16 = round(sum(TOTWGT_Ec3, na.rm = TRUE),2),
            WS16 = round(sum(SENWGT_Ec3, na.rm = TRUE),0),
            JK16 = n_distinct(JKZONES),
            n = n()) %>% knitr::kable()

#------Student Latinam questionnaire ---------
ISLC3 <- ISLC3 %>%  group_by(COUNTRY, cycle, questL) %>% 
  mutate(SENWGT_Lc3 = (TOTWGT_Lc3/sum(TOTWGT_Lc3))*1000) %>% ungroup()
ISLC3 %>% dplyr::select(TOTWGT_Lc3, SENWGT_Lc3, JKZONES, COUNTRY, cycle, questL) %>%
  group_by(COUNTRY, cycle, questL) %>% 
  summarise(W16 = round(sum(TOTWGT_Lc3, na.rm = TRUE),2),
            WS16 = round(sum(SENWGT_Lc3, na.rm = TRUE),0),
            JK16 = n_distinct(JKZONES),
            n = n()) %>% knitr::kable()

#------Stratus with only one school------------
ISGC3 %>% dplyr::select(JKZONES, COUNTRY, IDSCHOOL, cycle, questG) %>% group_by(COUNTRY, cycle, questG, JKZONES) %>% 
  summarise(n_schools = n_distinct(IDSCHOOL)) %>% group_by(cycle, COUNTRY, n_schools) %>% count() %>% filter(n_schools == 1)

#------Teacher general questionnaire ---------
ITGC3 <- ITGC3 %>% group_by(COUNTRY, cycle, questT) %>% 
  mutate(SENWGT_Tc3 = (TOTWGT_Tc3/sum(TOTWGT_Tc3))*1000) %>% ungroup()
ITGC3 %>% dplyr::select(TOTWGT_Tc3, SENWGT_Tc3, COUNTRY, cycle, questT) %>% 
  group_by(COUNTRY, cycle, questT) %>% 
  summarise(w16 = round(sum(TOTWGT_Tc3, na.rm = TRUE),2),
            WS16 = round(sum(SENWGT_Tc3, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()

#------School general questionnaire ---------
ICGC3 <- ICGC3 %>% group_by(COUNTRY, cycle, questC) %>% 
  mutate(SENWGT_Cc3 = (TOTWGT_Cc3/sum(TOTWGT_Cc3))*1000) %>% ungroup()
ICGC3 %>% dplyr::select(TOTWGT_Cc3, SENWGT_Cc3, COUNTRY, cycle, questC) %>%
  group_by(COUNTRY, cycle, questC) %>% 
  summarise(w16 = round(sum(TOTWGT_Cc3, na.rm = TRUE),2),
            WS16 = round(sum(SENWGT_Cc3, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()
```


```{r codebooks, eval=FALSE}

#Joining Questionnaires for Students 
tabISG3 <- read_xlsx("ICCS2016MS_Codebook.xlsx", sheet = "ISGC3")
tabISG3 <- tabISG3 %>% dplyr::select(ID,VariableC3, VariableC2, VariableC1, VariableName, Domain, Construct, Label, `Value Scheme Detailed`) %>% mutate(Dataset = "ISG")
tabISE3 <- read_xlsx("ICCS2016MS_Codebook.xlsx", sheet = "ISEC3")
tabISE3 <- tabISE3 %>% dplyr::select(ID,VariableC3, VariableC2, VariableC1, VariableName, Domain, Construct, Label, `Value Scheme Detailed`) %>% mutate(Dataset = "ISE")
tabISL3 <- read_xlsx("ICCS2016MS_Codebook.xlsx", sheet = "ISLC3")
tabISL3 <- tabISL3 %>% dplyr::select(ID,VariableC3, VariableC2, VariableC1, VariableName, Domain, Construct, Label, `Value Scheme Detailed`) %>% mutate(Dataset = "ISL")
tabITG3 <- read_xlsx("ICCS2016MS_Codebook.xlsx", sheet = "ITGC3")
tabITG3 <- tabITG3 %>% dplyr::select(ID,VariableC3, VariableC2, VariableC1, VariableName, Domain, Construct, Label, `Value Scheme Detailed`) %>% mutate(Dataset = "ITG")
tabICG3 <- read_xlsx("ICCS2016MS_Codebook.xlsx", sheet = "ICGC3")
tabICG3 <- tabICG3 %>% dplyr::select(ID,VariableC3, VariableC2, VariableC1, VariableName, Domain, Construct, Label, `Value Scheme Detailed`) %>% mutate(Dataset = "ICG")

VarsToUse <- tabISG3 %>% rbind(tabISE3) %>% rbind(tabISL3) %>% rbind(tabITG3) %>% rbind(tabICG3)
VarsToUse <- VarsToUse %>% filter(!is.na(Construct))
rm("tabISG3", "tabISE3", "tabISL3", "tabITG3", "tabICG3")


idS <- VarsToUse %>% filter(Dataset == "ISG" & Construct == "ID Variables" & !VariableName %in% c("IDGRADE", "IDPOP", "IDBOOK")) %>% dplyr::select(VariableName) %>%  pull()
idT <- VarsToUse %>% filter(Dataset == "ITG" & Construct == "ID Variables" & !VariableName %in% c("IDGRADE")) %>% dplyr::select(VariableName) %>%  pull()
idC <- VarsToUse %>% filter(Dataset == "ICG" & Construct == "ID Variables" & !VariableName %in% c("IDGRADE")) %>% dplyr::select(VariableName) %>%  pull()

```

```{r mergedata, eval=FALSE}
repet <- c("SAGE", "SGENDER", "S_GENDER", "S_AGE") # repeated in datasets
addvar <- c( "cycle", "questG", "questL", "questE", "questT", "questC", #created variables added to dataset
             "TOTWGT_Gc1", "SENWGT_Gc1", "TOTWGT_Gc2", "SENWGT_Gc2", "TOTWGT_Gc3", "SENWGT_Gc3",
                                         "TOTWGT_Ec2", "SENWGT_Ec2", "TOTWGT_Ec3", "SENWGT_Ec3",
                                         "TOTWGT_Lc2", "SENWGT_Lc2", "TOTWGT_Lc3", "SENWGT_Lc3",
                                         "TOTWGT_Tc2", "SENWGT_Tc2", "TOTWGT_Tc3", "SENWGT_Tc3",
             "TOTWGT_Cc1", "SENWGT_Cc1", "TOTWGT_Cc2", "SENWGT_Cc2", "TOTWGT_Cc3", "SENWGT_Cc3", "JKZONES") 
 
#Merging student questionnaires same cycle, General + European + Latin American
varsC1 <- VarsToUse %>% filter(!is.na(VariableC1) & Dataset %in% c("ISG", "ISE", "ISL")) %>% dplyr::select(VariableC1) %>% pull()
varsC2 <- VarsToUse %>% filter(!is.na(VariableC2) & Dataset %in% c("ISG", "ISE", "ISL")) %>% dplyr::select(VariableC2) %>% pull()
varsC3 <- VarsToUse %>% filter(!is.na(VariableC3) & Dataset %in% c("ISG", "ISE", "ISL")) %>% dplyr::select(VariableC3) %>% pull()

if (is.data.frame(ISGC1)) ISC1 <- ISGC1[, colnames(ISGC1) %in% c(varsC1,addvar)]

if (is.data.frame(ISGC2) & is.data.frame(ISEC2)) {
  ISC2 <- ISGC2[, colnames(ISGC2) %in% c(varsC2, addvar)] %>% 
    full_join(ISEC2[, colnames(ISEC2) %in% c(varsC2[!varsC2 %in% repet], addvar)], by = c(idS)) #repeated added only in first cycle
}  
if (is.data.frame(ISC2) & is.data.frame(ISLC2))  {
  ISC2 <- ISC2 %>% 
    full_join(ISLC2[, colnames(ISLC2) %in% c(varsC2[!varsC2 %in% repet], addvar)], by = c(idS)) 
}

if (is.data.frame(ISGC3) & is.data.frame(ISEC3)) {
  ISC3 <- ISGC3[, colnames(ISGC3) %in% c(varsC3, addvar)] %>% 
    full_join(ISEC3[, colnames(ISEC3) %in% c(varsC3[!varsC3 %in% repet], addvar)], by = c(idS)) 
}  
if (is.data.frame(ISC3) & is.data.frame(ISLC3))  {
  ISC3 <- ISC3 %>% 
    full_join(ISLC3[, colnames(ISLC3) %in% c(varsC3[!varsC3 %in% repet], addvar)], by = c(idS)) 
}

#######Student files
# ISC2_r <- rename_cycle(ISC2)
# ISC3_r <- rename_cycle(ISC3)

#Setting (row bind) cycles for Students Questionnaires

if (!exists("ISC1")) ISC1 <- NULL
if (!exists("ISC2")) ISC2 <- NULL
if (!exists("ISC3")) ISC3 <- NULL
  
ISC <- ISC1 %>%
  sjmisc::add_rows(ISC2) %>%
  sjmisc::add_rows(ISC3) 

#######Teacher file
#Setting (row bind) cycles for Teacher Questionnaires
# ITGC2_r <- rename_cycle(ITGC2)
# ITGC3_r <- rename_cycle(ITGC3)

varsC1 <- VarsToUse %>% filter(!is.na(VariableC1) & Dataset == "ITG") %>% dplyr::select(VariableC1) %>% pull()
varsC2 <- VarsToUse %>% filter(!is.na(VariableC2) & Dataset == "ITG") %>% dplyr::select(VariableC2) %>% pull()
varsC3 <- VarsToUse %>% filter(!is.na(VariableC3) & Dataset == "ITG") %>% dplyr::select(VariableC3) %>% pull()

if (!is.data.frame(ITGC1)) ITGC1 <- NULL else ITGC1 <- ITGC1[, colnames(ITGC1) %in% c(varsC1, addvar)]
if (!is.data.frame(ITGC2)) ITGC2 <- NULL else ITGC2 <- ITGC2[, colnames(ITGC2) %in% c(varsC2, addvar)]
if (!is.data.frame(ITGC3)) ITGC3 <- NULL else ITGC3 <- ITGC3[, colnames(ITGC3) %in% c(varsC3, addvar)]
 
ITG <- ITGC1 %>%
  sjmisc::add_rows(ITGC2) %>%
  sjmisc::add_rows(ITGC3) 

########School file
#Merging cycles for School Questionnaires
# ICGC2_r <- rename_cycle(ICGC2)
# ICGC3_r <- rename_cycle(ICGC3)

varsC1 <- VarsToUse %>% filter(!is.na(VariableC1) & Dataset == "ICG") %>% dplyr::select(VariableC1) %>% pull()
varsC2 <- VarsToUse %>% filter(!is.na(VariableC2) & Dataset == "ICG") %>% dplyr::select(VariableC2) %>% pull()
varsC3 <- VarsToUse %>% filter(!is.na(VariableC3) & Dataset == "ICG") %>% dplyr::select(VariableC3) %>% pull()

if (!is.data.frame(ICGC1)) ICGC1 <- NULL else ICGC1 <- ICGC1[, colnames(ICGC1) %in% c(varsC1, addvar)]
if (!is.data.frame(ICGC2)) ICGC2 <- NULL else ICGC2 <- ICGC2[, colnames(ICGC2) %in% c(varsC2, addvar)]
if (!is.data.frame(ICGC3)) ICGC3 <- NULL else ICGC3 <- ICGC3[, colnames(ICGC3) %in% c(varsC3, addvar)]
 
ICG <- ICGC1 %>%
  sjmisc::add_rows(ICGC2) %>%
  sjmisc::add_rows(ICGC3) 

#ICCS <- ISC %>% full_join(ITG, by = c("cycle", idC)) %>% full_join(ICG, by = c("cycle", idC))

# rm(list = c("ISGC1","ISGC2","ISEC2","ISLC2","ISGC3","ISEC3","ISLC3"))
# rm(list = c("ISC1","ISC2", "ISC3"))
# rm(list = c("ITGC1","ITGC2", "ITGC3"))
# rm(list = c("ICGC1","ICGC2", "ICGC3"))
# rm(list = c("repet","idT", "idC", "idS"))

#rm(list = c("ISC2_r", "ISC3_r"))
#rm(list = c("ITGC2_r", "ITGC3_r"))
#rm(list = c("ICGC2_r", "ICGC3_r"))


  
```

**Weights and sample size**  

The number of observations available for each cycle is in the following tables for each questionnaire, Student, Teacher and School.
*n\** corresponds to the effective sample size, *w\** to the total weight and *w\*s* the senate weight (sum up 1000 for each country).  

```{r Saveddata, results='asis'}

#save(VarsToUse, ISC, ITG, ICG, file = "ICCSAll.RData")

rm(list=setdiff(ls(), c("Itemdesc", "years")))
load("ICCSAll.RData")

Scales <- c(VarsToUse %>%  filter(Domain == "Scales" & Dataset %in% c("ISG","ISE")) %>% select(VariableC1) %>% na.omit() %>% pull(),
            VarsToUse %>%  filter(Domain == "Scales" & Dataset %in% c("ISG","ISE")) %>% select(VariableC2) %>% na.omit() %>% pull(),
            VarsToUse %>%  filter(Domain == "Scales" & Dataset  %in% c("ISG","ISE")) %>% select(VariableC3) %>% na.omit() %>% pull())

Indices <- c(VarsToUse %>%  filter(Domain == "Indice" & Dataset  %in% c("ISG","ISE")) %>% select(VariableC1) %>% na.omit() %>% pull(),
            VarsToUse %>%  filter(Domain == "Indice" & Dataset  %in% c("ISG","ISE")) %>% select(VariableC2) %>% na.omit() %>% pull(),
            VarsToUse %>%  filter(Domain == "Indice" & Dataset %in% c("ISG","ISE")) %>% select(VariableC3) %>% na.omit() %>% pull())

Id <- VarsToUse %>%  filter(Construct == "ID Variables" & Dataset == "ISG") %>% select(VariableName) %>% na.omit() %>% pull()

Gender <- c(VarsToUse %>%  filter(Construct %in% "Student gender") %>% select(VariableC1) %>% na.omit() %>% pull(),
              VarsToUse %>%  filter(Construct %in% "Student gender") %>% select(VariableC2) %>% na.omit() %>% pull(),
              VarsToUse %>%  filter(Construct %in% "Student gender") %>% select(VariableC3) %>% na.omit() %>% pull())


Sample <-  c(VarsToUse %>%  filter(Construct %in% "Weights" & Dataset == "ISG") %>% select(VariableC1) %>% na.omit() %>% pull(),
             VarsToUse %>%  filter(Construct %in% "Weights" & Dataset == "ISG") %>% select(VariableC2) %>% na.omit() %>% pull(),
             VarsToUse %>%  filter(Construct %in% "Weights" & Dataset == "ISG") %>% select(VariableC3) %>% na.omit() %>% pull())



cat(' \n')
cat("\n")
ISC %>% dplyr::select(TOTWGT_Gc1, SENWGT_Gc1, IDSCHOOL, JKZONES, COUNTRY, cycle, questG) %>% 
  filter(!is.na(TOTWGT_Gc1)) %>% 
  group_by(COUNTRY, questG) %>% 
  summarise(w99 = round(sum(TOTWGT_Gc1, na.rm = TRUE),0),
            w99s =round(sum(SENWGT_Gc1, na.rm = TRUE),0),
            nStr99 = n_distinct(JKZONES),
            nSch99 = n_distinct(IDSCHOOL),
            nStu99 = n()
            ) %>% 
  full_join(ISC %>% dplyr::select(TOTWGT_Gc2, SENWGT_Gc2, IDSCHOOL, JKZONES, COUNTRY, cycle, questG) %>% 
                    filter(!is.na(TOTWGT_Gc2)) %>% 
                    group_by(COUNTRY, questG) %>% 
                    summarise(w09 = round(sum(TOTWGT_Gc2, na.rm = TRUE),0),
                              w09s =sum(SENWGT_Gc2, na.rm = TRUE),
                              nStr09 = n_distinct(JKZONES),
                              nSch09 = n_distinct(IDSCHOOL),
                              nStu09 = n()),by = c("COUNTRY", "questG")) %>% 
  full_join(ISC %>% dplyr::select(TOTWGT_Gc3, SENWGT_Gc3, IDSCHOOL, JKZONES, COUNTRY, cycle, questG) %>% 
                    filter(!is.na(TOTWGT_Gc3)) %>% 
                    group_by(COUNTRY, questG) %>% 
                    summarise(w16 = round(sum(TOTWGT_Gc3, na.rm = TRUE),0),
                              w16s =sum(SENWGT_Gc3, na.rm = TRUE),
                              nStr16 = n_distinct(JKZONES),
                              nSch16 = n_distinct(IDSCHOOL),
                              nStu16 = n()),by = c("COUNTRY", "questG")) %>% 
  arrange(COUNTRY) %>% 
  knitr::kable(caption = "Student questionnaires")
cat('  \n')
cat("\n")
ITG %>% dplyr::select(TOTWGT_Tc2,SENWGT_Tc2, IDSCHOOL, COUNTRY, cycle, questT) %>% 
  filter(!is.na(TOTWGT_Tc2)) %>% 
  group_by(COUNTRY, questT) %>% 
  summarise(nTea99 = NA,
            nSch99 = NA,
            w99 = NA,
            w99s =NA,
            nTea09 = n(),
            nSch09 = n_distinct(IDSCHOOL),
            w09 = sum(TOTWGT_Tc2, na.rm = TRUE),
            w09s =sum(SENWGT_Tc2, na.rm = TRUE)) %>% 
  full_join(ITG %>% dplyr::select(TOTWGT_Tc3, SENWGT_Tc3, IDSCHOOL, COUNTRY, cycle, questT) %>% 
                    filter(!is.na(TOTWGT_Tc3)) %>% 
                    group_by(COUNTRY, questT) %>% 
                    summarise(nTea16 = n(),
                              nSch16 = n_distinct(IDSCHOOL),
                              w16 = sum(TOTWGT_Tc3, na.rm = TRUE),
                              w16s =sum(SENWGT_Tc3, na.rm = TRUE)),by = c("COUNTRY", "questT")) %>% 
  arrange(COUNTRY) %>% 
  knitr::kable(caption = "Teacher questionnaires")
cat('  \n')
cat("\n")
ICG %>% dplyr::select(TOTWGT_Cc1,SENWGT_Cc1, COUNTRY, cycle, questC) %>% 
  filter(!is.na(TOTWGT_Cc1)) %>% 
  group_by(COUNTRY, questC) %>% 
  summarise(nSch99 = n(),
            w99 = sum(TOTWGT_Cc1, na.rm = TRUE),
            w99s =round(sum(SENWGT_Cc1, na.rm = TRUE),0)) %>% 
  full_join(ICG %>% dplyr::select(TOTWGT_Cc2, SENWGT_Cc2, COUNTRY, cycle, questC) %>% 
                      filter(!is.na(TOTWGT_Cc2)) %>% 
                      group_by(COUNTRY, questC) %>% 
                      summarise(nSch09 = n(),
                      w09 = sum(TOTWGT_Cc2, na.rm = TRUE),
                      w09s =sum(SENWGT_Cc2, na.rm = TRUE)), by = c("COUNTRY", "questC")) %>% 
              full_join(ICG %>% dplyr::select(TOTWGT_Cc3, SENWGT_Cc3, COUNTRY, cycle, questC) %>% 
                    filter(!is.na(TOTWGT_Cc3)) %>% 
                    group_by(COUNTRY, questC) %>% 
                    summarise(nSch16 = n(),
                              w16 = sum(TOTWGT_Cc3, na.rm = TRUE),
                              w16s =sum(SENWGT_Cc3, na.rm = TRUE)), by = c("COUNTRY", "questC")) %>% 
  arrange(COUNTRY) %>% 
  knitr::kable(caption = "School questionnaires")

#colnames(ISC)

```

# Description of variables  {.tabset .tabset-fade .tabset-pills}

In this section items available in each data set regarding the constructs of interest are described. Barplots are drawn by country using their respective weights. The frequencies are differentiated by Gender and Total sample.    
The indexed of each respective scale are also plotted in a violin diagram, orderer by the weighted mean of each country. The boxplot of the distribution of the data is also included. Dotted line represent the weighted mean for each subgroup and Total.  
Each cycle can be seen in each tab in this section.
 

```{r descriptive, fig.height = 8, fig.width = 7, results = 'asis', fig.show='asis'}

ISC_desc <- ISC %>% select(all_of(Id), all_of(Scales), all_of(Indices), all_of(Sample), all_of(Gender))

source("1.Descriptive_Analysis.R")
rm(ISC_desc)
```

# Confirmatory Factor Analysis (CFA)  {.tabset .tabset-fade .tabset-pills}

In this section, a confirmatory factor analysis for the three scales analysed is performed, using weights and complexity of the sample was taken into account. Invariance analysis was also performed to Gender groups and Country groups. The loading od each country in the specific scale are plot with their respective confidence interval.    
Each cycle can be seen in each tab in this section. Finally, last tab show the scores obtained by each model, which are saved and used in the following sections. Latin American countries questionnaires did not include Immigration scale in 2016, the model for this countries only include remaining two scales.  

```{r cfa, fig.height = 11, fig.width = 9, results = 'asis'}

ISC$IDJK <- factor(paste0(ISC$IDCNTRY, ISC$JKZONES))
ISC$IDCL <- factor(paste0(ISC$IDCNTRY, ISC$JKZONES, ISC$IDSCHOOL))
sampleID <- c("IDJK", "IDCL", Sample)

ISC_cfa <- ISC %>% select(all_of(Id), all_of(Scales), all_of(Sample), all_of(sampleID), all_of(Gender))

source("2.cfa.R")

ISC_lv <- ISC[,!colnames(ISC) %in% Scales] %>% left_join(ISC_cfa, by = all_of(Id))
#save(ISC_lv, VarsToUse, file = "ICCSAll_lv.RData")
rm(ISC_cfa)
```

