---
title: "Attitudes toward equality - part 2"
author: "Pamela Inostroza Fernandez"
date: "December 2020"
output: 
  html_document:
    keep_md: true
    toc: TRUE
    toc_depth: 1
    toc_float: 
      collapsed: true
    number_sections: true
    theme: united
    highlight: tango
editor_options: 
  chunk_output_type: console
---

```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(readxl)
library(tidyverse)
library(sjPlot)

options(scipen = 999)
options(knitr.kable.NA = '')

#setwd("C:/Users/pamel/OneDrive - KU Leuven/Master in Statistics/Master Thesis/")
```  

# Standardization {.tabset .tabset-fade .tabset-pills}

The standardization of independent continuous variables, the scale was adjusted for each cycle the way that the minimum value was 0 and maximum value was 100.  
$z = \frac{x - min(x)}{max(x) - min(x)}*100$

For categorical variables, codification of similar categories was performed, maintaining the categories used in the last cycle study in 2016.  

```{r data, fig.height = 8, fig.width = 7, results = 'asis', fig.show='asis'}
#setwd("C:/Users/pamel/OneDrive - KU Leuven/Master in Statistics/Master Thesis/Data_analysis")
Countries <- read_xlsx("Metadata.xlsx", sheet = "CNT")
Files <- read_xlsx("Metadata.xlsx", sheet = "Files")
Itemdesc <- read_xlsx("Items scales.xlsx", sheet = "Scales")
CNTa <- c("DNK", "FIN", "NOR", "SWE")
CNTb <- c("BFL", "NLD")
CNTc <- c("BGR", "EST", "LVA", "LTU", "HRV", "SVN")
CNTd <- c("ITA", "MLT")
CNTe <- c("CHL", "PER", "COL", "DOM", "MEX")
CNT <- c(CNTa, CNTb, CNTc, CNTd, CNTe)
# c(AUS", "BFL", "BGR", "CHE", "CHL", "COL", "CYP", "CZE", "DEU", "DNK", "DOM", "ENG", "ESP", "EST", "FIN", "FRA", "GRC", "HKG", "HRV", "HUN", "ISR", "ITA", "KOR", "LTU", "LVA", "MEX", "MLT", "NLD", "NOR", "PER", "POL", "PRT", "ROM", "RUS", "SRB", "SVK", "SVN", "SWE", "TWN", "USA") CNTb #

years <- Countries %>% filter(AlphaCode %in% CNT & !is.na(Part)) %>% dplyr::select(Country, AlphaCode, year) 

load(file = "ICCSAll_lv.RData")

Scales <- c(paste0(VarsToUse %>%  filter(Domain == "Scales" & Dataset %in% c("ISG","ISE")) %>% select(VariableC1) %>% 
                     na.omit() %>% pull(),"."),
            VarsToUse %>%  filter(Domain == "Scales" & Dataset %in% c("ISG","ISE")) %>% select(VariableC2) %>% na.omit() %>% pull(),
            VarsToUse %>%  filter(Domain == "Scales" & Dataset  %in% c("ISG","ISE")) %>% select(VariableC3) %>% na.omit() %>% pull())

Scalesr <-c(ifelse(Scales %in% c("BS4G6.","BS4G9.","BS4G13.","IS2P24C","IS2P24D","IS2P24F","IS3G24C","IS3G24D","IS3G24F"), 
                   paste0(Scales,"_r"), Scales))
            
Indicfa <- c("Gend_Equal", "Immi_Equal", "Ethn_Equal")

Id <- VarsToUse %>%  filter(Construct == "ID Variables" & Dataset == "ISG") %>% select(VariableName) %>% na.omit() %>% pull()

Sample <-  c(VarsToUse %>%  filter(Construct %in% "Weights" & Dataset == "ISG") %>% select(VariableC1) %>% na.omit() %>% pull(),
             VarsToUse %>%  filter(Construct %in% "Weights" & Dataset == "ISG") %>% select(VariableC2) %>% na.omit() %>% pull(),
             VarsToUse %>%  filter(Construct %in% "Weights" & Dataset == "ISG") %>% select(VariableC3) %>% na.omit() %>% pull())

Man_cate0 <- c(VarsToUse %>%  filter(Domain %in% "Background questionnaires" & Dataset == "ISG") %>% select(VariableC1) %>% na.omit() %>% pull(),
              VarsToUse %>%  filter(Domain %in% "Background questionnaires" & Dataset == "ISG") %>% select(VariableC2) %>% na.omit() %>% pull(),
              VarsToUse %>%  filter(Domain %in% "Background questionnaires" & Dataset == "ISG") %>% select(VariableC3) %>% na.omit() %>% pull())

Man_cont0 <- c(VarsToUse %>%  filter(Domain %in% "Contextual" & Dataset == "ISG") %>% select(VariableC1) %>% na.omit() %>% pull(),
              VarsToUse %>%  filter(Domain %in% "Contextual" & Dataset == "ISG") %>% select(VariableC2) %>% na.omit() %>% pull(),
              VarsToUse %>%  filter(Domain %in% "Contextual" & Dataset == "ISG") %>% select(VariableC3) %>% na.omit() %>% pull())

Scores <- VarsToUse %>%  filter(Construct %in% "Scores" & Dataset == "ISG") %>% select(VariableName) %>% na.omit() %>% pull()

ISC_rec <- ISC_lv %>% select(all_of(Id), all_of(Man_cont0), all_of(Indicfa), all_of(Man_cate0), all_of(Sample), all_of(Scalesr))
source("3.Recod_var_for_modelling.R")

ISC_lvR <- ISC_lv %>% select(-all_of(Sample), -all_of(Man_cate0), -all_of(Man_cont0), -all_of(Indicfa)) %>% 
  left_join(ISC_rec, by = all_of(Id))
rm(ISC_rec)

#save(ISC_lvR, VarsToUse, file = "ICCSAll_lvR.RData")
```

# Multilevel modelling (MLM)  {.tabset .tabset-fade .tabset-pills}

In this section a multilevel model was performed to evaluate the variability of the scale considering the nested structure of the data. The first model use the three cycles of CIVED/ICCS as a level, followed by Country level and finally School level.
Next, The analysis is performed to all countries participating in each cycle separately, using country and school level. 
Results are obtained for the models indicated using Null model followed by the model with some explanatory variables at the student level. 

Dependant variables:  

Ethn_Equal: Attitudes toward equal rights for all ethnic or racial groups calculated by CFA (min = 0, max = 100)   
Gend_Equal: Attitudes toward gender equality calculated by CFA  (min = 0, max = 100) 
Immi_Equal: Attitudes toward equal rights for immigrants calculated by CFA (min = 0, max = 100) 

Explanatory variables:  

T_AGE: Age of the student   
T_GENDER: Gender of the student [0 = Boy(ref), 1 = Girl]   
T_RELIG: Student's religious affiliation [0 = No Religion(ref), 1 = Religion] 
T_IMMGR: Immigration status [0 = Native(ref), 1 = Immigrant]    
T_HOMELIT: Home literacy resources [0 = 0-10 books(ref), 1 = 11-25 books, 2 = 26-100 books, 3 = 101-200 books, 4 = More than 200 books]  
T_HISEI: Highest parental occupational status (min = 0, max = 100)   
T_NISB: National index of socioeconomic background  (min = 0, max = 100)

The function used is $lmer(Dep ~ Indep + (1|cycle) + (1|cycle:COUNTRY) + (1|cycle:COUNTRY:IDSCHOOL), data=data, weights=SENWGT,  REML=FALSE)$ for the three level model and 
$lmer(Dep ~ Indep + (1|COUNTRY) + (1|COUNTRY:IDSCHOOL), data=data, weights=SENWGT,  REML=FALSE)$ for the two level model.  

```{r mlm, fig.height = 9, fig.width = 7, results = 'asis'}
load("ICCSAll_lvR.RData")

Man_cate <- VarsToUse %>%  filter(Domain %in% "Background questionnaires" & Dataset == "ISG") %>% select(VariableName) %>% pull()
Man_cont <- VarsToUse %>%  filter(Domain %in% "Contextual" & Dataset == "ISG") %>% select(VariableName) %>% pull() %>% na.omit()
sampleID <- c("IDJK", "IDCL")

source("4.mlm.R")

cat('\n')
cat('\n')
cat('## Two level model: School nested in countries by cycles  \n')
cat('\n')
cat('\n')
cat('### Null model  \n')
cat('\n')
cat('\n')
t2
t3
t4
cat('\n')
cat('\n')
cat('### Model with independent variables  \n')
cat('\n')
cat('\n')
b11
b21
b31
cat('\n')
cat('\n')
cat('\n')
cat('\n')
cat('## Three level model: School nested in countries and in cycles  \n')
cat('\n')
cat('\n')
cat('### Null model  \n')
t1
cat('\n')
cat('\n')
cat('### Model with independent variables  \n')
cat('\n')
cat('\n')
t5
cat('\n')
cat('\n')
```

#  Log linear model / Poisson regression {.tabset .tabset-fade .tabset-pills}
 
Contingency table used for log linear model using Poisson distribution using four categories in response variables, *Strongly disagree*, *Disagree*, *Agree*, *Strongly agree*.  
The function used is glm() using svydesign() to account for nested data, cluster and weights. The design was defined as $svydesign(ids = ~IDSCHOOL, weights = ~SENWGT, strata = ~IDCNTRY, nest = TRUE, data=data)$  and 
$svyglm(formula = , design = survey.design, family = poisson, data = data)$.    

```{r lgn, results = 'asis'}
Scales <- c(VarsToUse %>%  filter(Domain == "Scales" & Dataset %in% c("ISG","ISE")) %>% select(VariableName) %>% na.omit() %>% pull())
sampleID <- c("IDJK", "IDCL", "SENWGT")

source("5.logistic_loglin.R")

cat('## Attitudes toward equal rights for immigrants \n')
cat("  \n")
cat("  \n")
ll11
cat("  \n")
cat("  \n")
ll12
cat("  \n")
cat("  \n")
ll13
cat("  \n")
cat("  \n")
ll14
cat("  \n")
cat("  \n")
ll15
cat("  \n")
cat("  \n")
cat('## Attitudes toward equal rights for gender \n')
cat("  \n")
cat("  \n")
ll21
cat("  \n")
cat("  \n")
ll22
cat("  \n")
cat("  \n")
ll23
cat("  \n")
cat("  \n")
ll24
cat("  \n")
cat("  \n")
ll25
cat("  \n")
cat("  \n")
ll26
cat("  \n")
cat("  \n")
ll27
cat("  \n")
cat("  \n")
cat('## Attitudes toward equal rights for ethnics \n')
cat("  \n")
cat("  \n")
ll31
cat("  \n")
cat("  \n")
ll32
cat("  \n")
cat("  \n")
ll33
cat("  \n")
cat("  \n")
ll34
cat("  \n")
cat("  \n")
ll35
cat("  \n")
cat("  \n")
```


# Logistic regression {.tabset .tabset-fade .tabset-pills}

Logistic regression was performed dichotomizing response variable in *Agree* and *Disagree* categories, being the last one the reference level.  

The function used is glm() using svydesign() to account for nested data, cluster and weights. The design was defined as $svydesign(ids = ~IDSCHOOL, weights = ~SENWGT, strata = ~IDCNTRY, nest = TRUE, data=data)$   
$svyglm(formula = , design = survey.design, family = binomial, data = data)$

```{r lga, results = 'asis'}

cat('## Attitudes toward equal rights for immigrants \n')
cat("  \n")
cat("  \n")
ll11
cat("  \n")
cat("  \n")
ll12
cat("  \n")
cat("  \n")
ll13
cat("  \n")
cat("  \n")
ll14
cat("  \n")
cat("  \n")
ll15
cat("  \n")
cat("  \n")
cat('## Attitudes toward equal rights for gender \n')
cat("  \n")
cat("  \n")
ll21
cat("  \n")
cat("  \n")
ll22
cat("  \n")
cat("  \n")
ll23
cat("  \n")
cat("  \n")
ll24
cat("  \n")
cat("  \n")
ll25
cat("  \n")
cat("  \n")
ll26
cat("  \n")
cat("  \n")
ll27
cat("  \n")
cat("  \n")
cat('## Attitudes toward equal rights for ethnics \n')
cat("  \n")
cat("  \n")
ll31
cat("  \n")
cat("  \n")
ll32
cat("  \n")
cat("  \n")
ll33
cat("  \n")
cat("  \n")
ll34
cat("  \n")
cat("  \n")
ll35
cat("  \n")
cat("  \n")
```


