---
title: "ICCS datafiles 1999/2009/2016/2022"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
editor_options: 
  chunk_output_type: console
---

# Files available

Selected countries and years (cycle) to analyse 

```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = 'C:/Users/pamel/OneDrive - KU Leuven/Master in Statistics/Master Thesis')
library(haven)
library(readxl)
library(tidyverse)
options(scipen = 999)
options(knitr.kable.NA = '')

setwd("C:/Users/pamel/OneDrive - KU Leuven/Master in Statistics/Master Thesis/")
sys.source("Data_analysis/functions.R", envir = knitr::knit_global())

```  

**Participant countries**  

a. Nordic Countries: Denmark, Finland, Norway, Sweden.  
b. Western European Countries: Belgium (Flemish), The Netherlands.  
c. Central and Eastern European Countries: Bulgaria, Estonia, Latvia, Lithuania, Croatia, Slovenia.  
d. Southern European Countries: Italy, Malta.  
e. Latin American Countries: Chile, Peru, Colombia, Dominican Republic, Mexico.  

```{r data}
Countries <- read_xlsx("Data_analysis/Metadata.xlsx", sheet = "CNT")
Files <- read_xlsx("Data_analysis/Metadata.xlsx", sheet = "Files")
Scales <- read_xlsx("Data_analysis/Items scales.xlsx", sheet = "Scales")
CNTa <- c("DNK", "FIN", "NOR", "SWE")
CNTb <- c("BFL", "NLD")
CNTc <- c("BGR", "EST", "LVA", "LTU", "HRV", "SVN")
CNTd <- c("ITA", "MLT")
CNTe <- c("CHL", "PER", "COL", "DOM", "MEX")
CNT <- c(CNTa, CNTb, CNTc, CNTd, CNTe)
# c(AUS", "BFL", "BGR", "CHE", "CHL", "COL", "CYP", "CZE", "DEU", "DNK", "DOM", "ENG", "ESP", "EST", "FIN", "FRA", "GRC", "HKG", "HRV", "HUN", "ISR", "ITA", "KOR", "LTU", "LVA", "MEX", "MLT", "NLD", "NOR", "PER", "POL", "PRT", "ROM", "RUS", "SRB", "SVK", "SVN", "SWE", "TWN", "USA") CNTb #

years <- Countries %>% filter(AlphaCode %in% CNT & !is.na(Part)) %>% dplyr::select(Country, AlphaCode, year) 

```

```{r namesfiles, comment=""}
filenames <- NULL
print("Countries selected and year participation in ICCS:")

for (cnt in CNT) {

  yearf <- years %>% filter(AlphaCode == cnt & year != 22) %>% arrange(as.numeric(year))
  
  print(paste0(unique(yearf$Country), " :", paste(sort(ifelse(yearf$year == "99", paste0("19",yearf$year), paste0("20",yearf$year))), collapse = " ")))

  for (yearn in yearf$year) {
 
    CountryEU <- Countries %>% filter(year == yearn & !is.na(EUQ)) %>% dplyr::select(AlphaCode)
    CountryLA <- Countries %>% filter(year == yearn & !is.na(LAQ)) %>% dplyr::select(AlphaCode) 
    Teacher <- Countries %>% filter(year == yearn & !is.na(ITG)) %>% dplyr::select(AlphaCode) 
    School <- Countries %>% filter(year == yearn & !is.na(ICG)) %>% dplyr::select(AlphaCode) 
    
    if (yearn == "99") Folder <- paste0("CivED19",yearn,"_IDB_SPSS_G8") else
      Folder <- paste0("ICCS20",yearn,"_IDB_SPSS")
    File <- Files %>% filter(!is.na(ToUse)) %>% dplyr::select(Filename)
    if (yearn == "99") cycle = "f2" else if (yearn == "09") cycle = "C2" else if (yearn == "16") cycle = "C3" else 
      if (yearn == "22") cycle = "C4"
    if (yearn == "99") {
      filenames <- c(filenames, paste0(Folder, "/Data/", "bs_", tolower(cnt), cycle,".sav"))
      if (cnt %in% Teacher$AlphaCode) filenames <- c(filenames, paste0(Folder, "/Data/", "bt_", tolower(cnt), cycle,".sav"))
      if (cnt %in% School$AlphaCode) filenames <- c(filenames, paste0(Folder, "/Data/", "bc_", tolower(cnt), cycle,".sav"))
    } else {
      if (cnt %in% CountryLA$AlphaCode) filenames <- c(filenames, paste0(Folder, "/Data/", "ISL",cnt,cycle,".sav"))
      if (cnt %in% CountryEU$AlphaCode) filenames <- c(filenames, paste0(Folder, "/Data/", "ISE",cnt,cycle,".sav")) 
      filenames <- c(filenames, paste0(Folder, "/Data/", "ISG",cnt,cycle,".sav"))
      if (cnt %in% Teacher$AlphaCode) filenames <- c(filenames, paste0(Folder, "/Data/", "ITG",cnt,cycle,".sav"))
      if (cnt %in% School$AlphaCode) filenames <- c(filenames, paste0(Folder, "/Data/", "ICG",cnt,cycle,".sav")) 
    }
  }
}
#order by questionnaire and cycle
filenames <- filenames[order(substr(filenames,24,26),substr(filenames,30,31))] 
rm(list = c("yearf", "cnt", "cycle", "Folder", "yearn", "File", "CountryEU", "CountryLA"))
```

```{r read_spss, eval=FALSE}
ICGC1 <- NULL
ICGC2 <- NULL
ICGC3 <- NULL
ITGC1 <- NULL
ITGC2 <- NULL
ITGC3 <- NULL
ISGC1 <- NULL
ISGC2 <- NULL
ISGC3 <- NULL
ISEC2 <- NULL
ISEC3 <- NULL
ISLC2 <- NULL
ISLC3 <- NULL

for (nc in 1:length(filenames)) {
  print(paste("nc:",filenames[nc]))
  if (substr(filenames[nc],24,26) == "ICG" | substr(filenames[nc],28,30) == "bc_") {
    if (substr(filenames[nc],34,35) == "f2") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))
      dataset_r <- dataset %>% rename_at(vars(colnames(dataset)), ~ toupper(colnames(dataset)))
      ICGC1 <- rbind(ICGC1, dataset_r)
    } else if (substr(filenames[nc],30,31) == "C2") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))
      ICGC2 <- rbind(ICGC2, dataset)
    } else if (substr(filenames[nc],30,31) == "C3") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))
      ICGC3 <- rbind(ICGC3, dataset)
    }
  }
  if (substr(filenames[nc],24,26) == "ITG" | substr(filenames[nc],28,30) == "bt_"){
    if (substr(filenames[nc],34,35) == "f2") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))
      dataset_r <- dataset %>% rename_at(vars(colnames(dataset)), ~ toupper(colnames(dataset)))
      ITGC1 <- rbind(ITGC1, dataset_r)
    } else if (substr(filenames[nc],30,31) == "C2") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))
      ITGC2 <- rbind(ITGC2, dataset)
    } else if (substr(filenames[nc],30,31) == "C3") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))
      ITGC3 <- rbind(ITGC3, dataset)
    }
  }
  
  if (substr(filenames[nc],24,26) == "ISG" | substr(filenames[nc],28,30) == "bs_"){
   if (substr(filenames[nc],34,35) == "f2") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))
      dataset_r <- dataset %>% rename_at(vars(colnames(dataset)), ~ toupper(colnames(dataset)))
      dataset_r$IMMIGMLE <- labelled(dataset_r$IMMIGMLE, labels =  c(INVALID = 97, OMITTED = 99), label = attr(dataset_r$IMMIGMLE, "label"))
      dataset_r$WOMRTMLE <- labelled(dataset_r$WOMRTMLE, labels =  c(INVALID = 97, OMITTED = 99), label = attr(dataset_r$WOMRTMLE, "label"))
      ISGC1 <- rbind(ISGC1, dataset_r)
    } else if (substr(filenames[nc],30,31) == "C2") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))
      ISGC2 <- rbind(ISGC2, dataset)
    } else if (substr(filenames[nc],30,31) == "C3") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))  
      ISGC3 <- rbind(ISGC3, dataset)
    }
  }
  
  if (substr(filenames[nc],24,26) == "ISE") {
    if (substr(filenames[nc],30,31) == "C2") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))
      ISEC2 <- rbind(ISEC2, dataset)
    } else if (substr(filenames[nc],30,31) == "C3") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))  
      ISEC3 <- rbind(ISEC3, dataset)
    }
  }
  if (substr(filenames[nc],24,26) == "ISL") {
    if (substr(filenames[nc],30,31) == "C2") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))
      ISLC2 <- rbind(ISLC2, dataset)
    } else if (substr(filenames[nc],30,31) == "C3") {
      dataset <- read_sav(file.path("Magda files/Data", filenames[nc]))  
      ISLC3 <- rbind(ISLC3, dataset)
    }
  }
}
ISGC1$cycle <- "C1"
ISGC2$cycle <- "C2"
ISGC3$cycle <- "C3"
ISEC2$cycle <- "C2"
ISEC3$cycle <- "C3"
ISLC2$cycle <- "C2"
ISLC3$cycle <- "C3"

ITGC1$cycle <- "C1"
ITGC2$cycle <- "C2"
ITGC3$cycle <- "C3"
ICGC1$cycle <- "C1"
ICGC2$cycle <- "C2"
ICGC3$cycle <- "C3"

ISGC1$questG <- "ISG"
ISGC2$questG <- "ISG"
ISGC3$questG <- "ISG"
ISEC2$questE <- "ISE"
ISEC3$questE <- "ISE"
ISLC2$questL <- "ISL"
ISLC3$questL <- "ISL"

ITGC1$questT <- "ITG"
ITGC2$questT <- "ITG"
ITGC3$questT <- "ITG"
ICGC1$questC <- "ICG"
ICGC2$questC <- "ICG"
ICGC3$questC <- "ICG"

ISGC1 <- ISGC1 %>% rename_at(vars(c("TOTWGT","SENWGT")), ~ c("TOTWGT_Gc1", "SENWGT_Gc1"))
ISGC2 <- ISGC2 %>% rename_at(vars(c("TOTWGTS","SENWGTS", "HOMELIT")), ~ c("TOTWGT_Gc2", "SENWGT_Gc2","SHOMELIT"))
ISGC3 <- ISGC3 %>% rename_at(vars(c("TOTWGTS")), ~ c("TOTWGT_Gc3"))

ISEC2 <- ISEC2 %>% rename_at(vars(c("TOTWGTS","SENWGTS")), ~ c("TOTWGT_Ec2", "SENWGT_Ec2"))
ISEC3 <- ISEC3 %>% rename_at(vars(c("TOTWGTS")), ~ c("TOTWGT_Ec3"))
ISLC2 <- ISLC2 %>% rename_at(vars(c("TOTWGTS","SENWGTS")), ~ c("TOTWGT_Lc2", "SENWGT_Lc2"))
ISLC3 <- ISLC3 %>% rename_at(vars(c("TOTWGTS")), ~ c("TOTWGT_Lc3"))

#ITGC1 <- ITGC1 %>% rename_at(vars(c()), ~ c("TOTWGT_Tc1", "SENWGT_Tc1"))
ITGC2 <- ITGC2 %>% rename_at(vars(c("TOTWGTT","SENWGTT")), ~ c("TOTWGT_Tc2", "SENWGT_Tc2"))
ITGC3 <- ITGC3 %>% rename_at(vars(c("TOTWGTT")), ~ c("TOTWGT_Tc3"))

ICGC1 <- ICGC1 %>% rename_at(vars(c("SCHWGT","STDWGT")), ~ c("TOTWGT_Cc1", "SENWGT_Cc1"))
ICGC2 <- ICGC2 %>% rename_at(vars(c("TOTWGTC")), ~ c("TOTWGT_Cc2"))
ICGC3 <- ICGC3 %>% rename_at(vars(c("TOTWGTC")), ~ c("TOTWGT_Cc3"))

#rm(list = c("dataset","nc","filenames"))

ISGC1 %>% dplyr::select(TOTWGT_Gc1,SENWGT_Gc1, COUNTRY, cycle, questG) %>% group_by(COUNTRY, cycle, questG) %>% 
  summarise(w99 = sum(TOTWGT_Gc1, na.rm = TRUE),
            WS99 = round(sum(SENWGT_Gc1, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()

ISGC2 <- ISGC2 %>% group_by(COUNTRY, cycle, questG) %>%
  mutate(SENWGT_Gc2 = (TOTWGT_Gc2/sum(TOTWGT_Gc2))*1000) %>% ungroup()
ISGC2 %>% dplyr::select(TOTWGT_Gc2, SENWGT_Gc2, COUNTRY, cycle, questG)  %>% 
  group_by(COUNTRY, cycle, questG) %>% 
  summarise(w09 = sum(TOTWGT_Gc2, na.rm = TRUE),
            w09s =sum(SENWGT_Gc2, na.rm = TRUE),
            n = n()) %>% knitr::kable()

ISGC3 <- ISGC3 %>% group_by(COUNTRY, cycle, questG) %>% 
  mutate(SENWGT_Gc3 = (TOTWGT_Gc3/sum(TOTWGT_Gc3))*1000) %>% ungroup()
ISGC3 %>% dplyr::select(TOTWGT_Gc3, SENWGT_Gc3, COUNTRY, cycle, questG) %>% 
  group_by(COUNTRY, cycle, questG) %>% 
  summarise(w16 = sum(TOTWGT_Gc3, na.rm = TRUE),
            w16s = sum(SENWGT_Gc3, na.rm = TRUE),
            n = n()) %>% knitr::kable()

ISEC2 <- ISEC2 %>% group_by(COUNTRY, cycle, questE) %>% 
  mutate(SENWGT_Ec2 = (TOTWGT_Ec2/sum(TOTWGT_Ec2))*1000) %>% ungroup()
ISEC2 %>% dplyr::select(TOTWGT_Ec2,SENWGT_Ec2, COUNTRY, cycle, questE) %>% 
  group_by(COUNTRY, cycle, questE) %>% 
  summarise(w09 = round(sum(TOTWGT_Ec2, na.rm = TRUE),2),
            WS09 = round(sum(SENWGT_Ec2, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()

ISEC3 <- ISEC3 %>% group_by(COUNTRY, cycle, questE) %>% 
  mutate(SENWGT_Ec3 = (TOTWGT_Ec3/sum(TOTWGT_Ec3))*1000) %>% ungroup()
ISEC3 %>% dplyr::select(TOTWGT_Ec3, SENWGT_Ec3, COUNTRY, cycle, questE) %>% 
  group_by(COUNTRY, cycle, questE) %>% 
  summarise(w16 = round(sum(TOTWGT_Ec3, na.rm = TRUE),2),
            WS16 = round(sum(SENWGT_Ec3, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()

ISLC2 <- ISLC2 %>% group_by(COUNTRY, cycle, questL) %>% 
  mutate(SENWGT_Lc2 = (TOTWGT_Lc2/sum(TOTWGT_Lc2))*1000) %>% ungroup()
ISLC2 %>% dplyr::select(TOTWGT_Lc2,SENWGT_Lc2, COUNTRY, cycle, questL) %>%
  group_by(COUNTRY, cycle, questL) %>%
  summarise(w09 = round(sum(TOTWGT_Lc2, na.rm = TRUE),2),
            WS09 = round(sum(SENWGT_Lc2, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()

ISLC3 <- ISLC3 %>%  group_by(COUNTRY, cycle, questL) %>% 
  mutate(SENWGT_Lc3 = (TOTWGT_Lc3/sum(TOTWGT_Lc3))*1000) %>% ungroup()
ISLC3 %>% dplyr::select(TOTWGT_Lc3, SENWGT_Lc3, COUNTRY, cycle, questL) %>%
  group_by(COUNTRY, cycle, questL) %>% 
  summarise(w16 = round(sum(TOTWGT_Lc3, na.rm = TRUE),2),
            WS16 = round(sum(SENWGT_Lc3, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()

# ITGC1 <- ITGC1 %>%  group_by(COUNTRY, cycle, questT) %>%
#   mutate(SENWGT_Tc1 = (TOTWGT_Tc1/sum(TOTWGT_Tc1))*1000) %>% ungroup()
# ITGC1 %>% dplyr::select(TOTWGT_Tc1,SENWGT_Tc1, COUNTRY, cycle, questT) %>%
#   group_by(COUNTRY, cycle, questT) %>%
#   summarise(w99 = round(sum(TOTWGT_Tc1, na.rm = TRUE),2),
#             WS99 = round(sum(SENWGT_Tc1, na.rm = TRUE),0),
#             n = n()) %>% knitr::kable()

ITGC2 <- ITGC2 %>%  group_by(COUNTRY, cycle, questT) %>% 
  mutate(SENWGT_Tc2 = (TOTWGT_Tc2/sum(TOTWGT_Tc2))*1000) %>% ungroup()
ITGC2 %>% dplyr::select(TOTWGT_Tc2,SENWGT_Tc2, COUNTRY, cycle, questT) %>%
  group_by(COUNTRY, cycle, questT) %>% 
  summarise(w09 = round(sum(TOTWGT_Tc2, na.rm = TRUE),2),
            WS09 = round(sum(SENWGT_Tc2, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()

ITGC3 <- ITGC3 %>% group_by(COUNTRY, cycle, questT) %>% 
  mutate(SENWGT_Tc3 = (TOTWGT_Tc3/sum(TOTWGT_Tc3))*1000) %>% ungroup()
ITGC3 %>% dplyr::select(TOTWGT_Tc3, SENWGT_Tc3, COUNTRY, cycle, questT) %>% 
  group_by(COUNTRY, cycle, questT) %>% 
  summarise(w16 = round(sum(TOTWGT_Tc3, na.rm = TRUE),2),
            WS16 = round(sum(SENWGT_Tc3, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()

ICGC1 <- ICGC1 %>%  group_by(COUNTRY, cycle, questC) %>% 
  mutate(SENWGT_Cc1 = (TOTWGT_Cc1/sum(TOTWGT_Cc1))*1000) %>% ungroup()
ICGC1 %>% dplyr::select(TOTWGT_Cc1,SENWGT_Cc1, COUNTRY, cycle, questC) %>%
   group_by(COUNTRY, cycle, questC) %>% 
  summarise(w99 = round(sum(TOTWGT_Cc1, na.rm = TRUE),2),
            WS99 = round(sum(SENWGT_Cc1, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()

ICGC2 <- ICGC2 %>% group_by(COUNTRY, cycle, questC) %>% 
  mutate(SENWGT_Cc2 = (TOTWGT_Cc2/sum(TOTWGT_Cc2))*1000) %>% ungroup()
ICGC2 %>% dplyr::select(TOTWGT_Cc2, SENWGT_Cc2, COUNTRY, cycle, questC) %>% 
  group_by(COUNTRY, cycle, questC) %>% 
  summarise(w09 = round(sum(TOTWGT_Cc2, na.rm = TRUE),2),
            WS09 = round(sum(SENWGT_Cc2, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()

ICGC3 <- ICGC3 %>% group_by(COUNTRY, cycle, questC) %>% 
  mutate(SENWGT_Cc3 = (TOTWGT_Cc3/sum(TOTWGT_Cc3))*1000) %>% ungroup()
ICGC3 %>% dplyr::select(TOTWGT_Cc3, SENWGT_Cc3, COUNTRY, cycle, questC) %>%
  group_by(COUNTRY, cycle, questC) %>% 
  summarise(w16 = round(sum(TOTWGT_Cc3, na.rm = TRUE),2),
            WS16 = round(sum(SENWGT_Cc3, na.rm = TRUE),0),
            n = n()) %>% knitr::kable()
```


```{r codebooks, eval=FALSE}

#Joining Questionnaires for Students 
tabISG3 <- read_xlsx("Data_analysis/ICCS2016MS_Codebook.xlsx", sheet = "ISGC3")
tabISG3 <- tabISG3 %>% dplyr::select(ID,VariableC3, VariableC2, VariableC1, Domain, Construct, Label, `Value Scheme Detailed`) %>% mutate(Dataset = "ISG")
tabISE3 <- read_xlsx("Data_analysis/ICCS2016MS_Codebook.xlsx", sheet = "ISEC3")
tabISE3 <- tabISE3 %>% dplyr::select(ID,VariableC3, VariableC2, VariableC1, Domain, Construct, Label, `Value Scheme Detailed`) %>% mutate(Dataset = "ISE")
tabISL3 <- read_xlsx("Data_analysis/ICCS2016MS_Codebook.xlsx", sheet = "ISLC3")
tabISL3 <- tabISL3 %>% dplyr::select(ID,VariableC3, VariableC2, VariableC1, Domain, Construct, Label, `Value Scheme Detailed`) %>% mutate(Dataset = "ISL")
tabITG3 <- read_xlsx("Data_analysis/ICCS2016MS_Codebook.xlsx", sheet = "ITGC3")
tabITG3 <- tabITG3 %>% dplyr::select(ID,VariableC3, VariableC2, VariableC1, Domain, Construct, Label, `Value Scheme Detailed`) %>% mutate(Dataset = "ITG")
tabICG3 <- read_xlsx("Data_analysis/ICCS2016MS_Codebook.xlsx", sheet = "ICGC3")
tabICG3 <- tabICG3 %>% dplyr::select(ID,VariableC3, VariableC2, VariableC1, Domain, Construct, Label, `Value Scheme Detailed`) %>% mutate(Dataset = "ICG")

VarsToUse <- tabISG3 %>% rbind(tabISE3) %>% rbind(tabISL3) %>% rbind(tabITG3) %>% rbind(tabICG3)
VarsToUse <- VarsToUse %>% filter(!is.na(Construct))
rm("tabISG3", "tabISE3", "tabISL3", "tabITG3", "tabICG3")


idS <- VarsToUse %>% filter(Dataset == "ISG" & Construct == "ID Variables" & !VariableC3 %in% c("IDGRADE", "IDPOP", "IDBOOK")) %>% dplyr::select(VariableC3) %>%  pull()
idT <- VarsToUse %>% filter(Dataset == "ITG" & Construct == "ID Variables" & !VariableC3 %in% c("IDGRADE")) %>% dplyr::select(VariableC3) %>%  pull()
idC <- VarsToUse %>% filter(Dataset == "ICG" & Construct == "ID Variables" & !VariableC3 %in% c("IDGRADE")) %>% dplyr::select(VariableC3) %>%  pull()

```

```{r mergedata, eval=FALSE}
repet <- c("SAGE", "SGENDER", "S_GENDER", "S_AGE")
addvar <- c( "cycle", "questG", "questL", "questE", "questT", "questC",
             "TOTWGT_Gc1", "SENWGT_Gc1", "TOTWGT_Gc2", "SENWGT_Gc2", "TOTWGT_Gc3", "SENWGT_Gc3",
                                         "TOTWGT_Ec2", "SENWGT_Ec2", "TOTWGT_Ec3", "SENWGT_Ec3",
                                         "TOTWGT_Lc2", "SENWGT_Lc2", "TOTWGT_Lc3", "SENWGT_Lc3",
                                         "TOTWGT_Tc2", "SENWGT_Tc2", "TOTWGT_Tc3", "SENWGT_Tc3",
             "TOTWGT_Cc1", "SENWGT_Cc1", "TOTWGT_Cc2", "SENWGT_Cc2", "TOTWGT_Cc3", "SENWGT_Cc3")
 
#Merging student questionnaires same cycle, General + European + Latin American
varsC1 <- VarsToUse %>% filter(!is.na(VariableC1) & Dataset %in% c("ISG", "ISE", "ISL")) %>% dplyr::select(VariableC1) %>% pull()
varsC2 <- VarsToUse %>% filter(!is.na(VariableC2) & Dataset %in% c("ISG", "ISE", "ISL")) %>% dplyr::select(VariableC2) %>% pull()
varsC3 <- VarsToUse %>% filter(!is.na(VariableC3) & Dataset %in% c("ISG", "ISE", "ISL")) %>% dplyr::select(VariableC3) %>% pull()

if (is.data.frame(ISGC1)) ISC1 <- ISGC1[, colnames(ISGC1) %in% c(varsC1,addvar)]

if (is.data.frame(ISGC2) & is.data.frame(ISEC2)) {
  ISC2 <- ISGC2[, colnames(ISGC2) %in% c(varsC2, addvar)] %>% 
    full_join(ISEC2[, colnames(ISEC2) %in% c(varsC2[!varsC2 %in% repet], addvar)], by = c("cycle", idS)) 
}  
if (is.data.frame(ISC2) & is.data.frame(ISLC2))  {
  ISC2 <- ISC2 %>% 
    full_join(ISLC2[, colnames(ISLC2) %in% c(varsC2[!varsC2 %in% repet], addvar)], by = c("cycle", idS)) 
}

if (is.data.frame(ISGC3) & is.data.frame(ISEC3)) {
  ISC3 <- ISGC3[, colnames(ISGC3) %in% c(varsC3, addvar)] %>% 
    full_join(ISEC3[, colnames(ISEC3) %in% c(varsC3[!varsC3 %in% repet], addvar)], by = c("cycle", idS)) 
}  
if (is.data.frame(ISC3) & is.data.frame(ISLC3))  {
  ISC3 <- ISC3 %>% 
    full_join(ISLC3[, colnames(ISLC3) %in% c(varsC3[!varsC3 %in% repet], addvar)], by = c("cycle", idS)) 
}

#######Student files
# ISC2_r <- rename_cycle(ISC2)
# ISC3_r <- rename_cycle(ISC3)

#Setting (row bind) cycles for Students Questionnaires

if (!exists("ISC1")) ISC1 <- NULL
if (!exists("ISC2")) ISC2 <- NULL
if (!exists("ISC3")) ISC3 <- NULL
  
ISC <- ISC1 %>%
  bind_rows(ISC2) %>%
  bind_rows(ISC3) 

#######Teacher file
#Setting (row bind) cycles for Teacher Questionnaires
# ITGC2_r <- rename_cycle(ITGC2)
# ITGC3_r <- rename_cycle(ITGC3)

varsC1 <- VarsToUse %>% filter(!is.na(VariableC1) & Dataset == "ITG") %>% dplyr::select(VariableC1) %>% pull()
varsC2 <- VarsToUse %>% filter(!is.na(VariableC2) & Dataset == "ITG") %>% dplyr::select(VariableC2) %>% pull()
varsC3 <- VarsToUse %>% filter(!is.na(VariableC3) & Dataset == "ITG") %>% dplyr::select(VariableC3) %>% pull()

if (!is.data.frame(ITGC1)) ITGC1 <- NULL else ITGC1 <- ITGC1[, colnames(ITGC1) %in% c(varsC1, addvar)]
if (!is.data.frame(ITGC2)) ITGC2 <- NULL else ITGC2 <- ITGC2[, colnames(ITGC2) %in% c(varsC2, addvar)]
if (!is.data.frame(ITGC3)) ITGC3 <- NULL else ITGC3 <- ITGC3[, colnames(ITGC3) %in% c(varsC3, addvar)]
 
ITG <- ITGC1 %>%
  bind_rows(ITGC2) %>%
  bind_rows(ITGC3) 

########School file
#Merging cycles for School Questionnaires
# ICGC2_r <- rename_cycle(ICGC2)
# ICGC3_r <- rename_cycle(ICGC3)

varsC1 <- VarsToUse %>% filter(!is.na(VariableC1) & Dataset == "ICG") %>% dplyr::select(VariableC1) %>% pull()
varsC2 <- VarsToUse %>% filter(!is.na(VariableC2) & Dataset == "ICG") %>% dplyr::select(VariableC2) %>% pull()
varsC3 <- VarsToUse %>% filter(!is.na(VariableC3) & Dataset == "ICG") %>% dplyr::select(VariableC3) %>% pull()

if (!is.data.frame(ICGC1)) ICGC1 <- NULL else ICGC1 <- ICGC1[, colnames(ICGC1) %in% c(varsC1, addvar)]
if (!is.data.frame(ICGC2)) ICGC2 <- NULL else ICGC2 <- ICGC2[, colnames(ICGC2) %in% c(varsC2, addvar)]
if (!is.data.frame(ICGC3)) ICGC3 <- NULL else ICGC3 <- ICGC3[, colnames(ICGC3) %in% c(varsC3, addvar)]
 
ICG <- ICGC1 %>%
  bind_rows(ICGC2) %>%
  bind_rows(ICGC3) 

#ICCS <- ISC %>% full_join(ITG, by = c("cycle", idC)) %>% full_join(ICG, by = c("cycle", idC))

# rm(list = c("ISGC1","ISGC2","ISEC2","ISLC2","ISGC3","ISEC3","ISLC3"))
# rm(list = c("ISC1","ISC2", "ISC3"))
# rm(list = c("ITGC1","ITGC2", "ITGC3"))
# rm(list = c("ICGC1","ICGC2", "ICGC3"))
# rm(list = c("repet","idT", "idC", "idS"))

#rm(list = c("ISC2_r", "ISC3_r"))
#rm(list = c("ITGC2_r", "ITGC3_r"))
#rm(list = c("ICGC2_r", "ICGC3_r"))

```

**Weights and sample size**  

```{r Saveddata, results='asis'}
#save(VarsToUse, ISC, ITG, ICG, file = "Data_analysis/ICCSAll.RData")


load("Data_analysis/ICCSAll.RData")
#load("Data_analysis/ICCS.RData")

cat('Student questionnaires  \n')
cat("\n")
ISC %>% dplyr::select(TOTWGT_Gc1, SENWGT_Gc1, COUNTRY, cycle, questG) %>% 
  filter(!is.na(TOTWGT_Gc1)) %>% 
  group_by(COUNTRY, questG) %>% 
  summarise(n99 = n(),
            w99 = sum(TOTWGT_Gc1, na.rm = TRUE),
            w99s =round(sum(SENWGT_Gc1, na.rm = TRUE),0)) %>% 
  full_join(ISC %>% dplyr::select(TOTWGT_Gc2, SENWGT_Gc2, COUNTRY, cycle, questG) %>% 
                    filter(!is.na(TOTWGT_Gc2)) %>% 
                    group_by(COUNTRY, questG) %>% 
                    summarise(n09 = n(),
                              w09 = sum(TOTWGT_Gc2, na.rm = TRUE),
                              w09s =sum(SENWGT_Gc2, na.rm = TRUE)),by = c("COUNTRY", "questG")) %>% 
  full_join(ISC %>% dplyr::select(TOTWGT_Gc3, SENWGT_Gc3, COUNTRY, cycle, questG) %>% 
                    filter(!is.na(TOTWGT_Gc3)) %>% 
                    group_by(COUNTRY, questG) %>% 
                    summarise(n16 = n(),
                              w16 = sum(TOTWGT_Gc3, na.rm = TRUE),
                              w16s =sum(SENWGT_Gc3, na.rm = TRUE)),by = c("COUNTRY", "questG")) %>% 
  arrange(COUNTRY) %>% 
  knitr::kable()
cat('Teacher questionnaires  \n')
cat("\n")
ITG %>% dplyr::select(TOTWGT_Tc2,SENWGT_Tc2, COUNTRY, cycle, questT) %>% 
  filter(!is.na(TOTWGT_Tc2)) %>% 
  group_by(COUNTRY, questT) %>% 
  summarise(n99 = NA,
            w99 = NA,
            w99s =NA,
            n09 = n(),
            w09 = sum(TOTWGT_Tc2, na.rm = TRUE),
            w09s =sum(SENWGT_Tc2, na.rm = TRUE)) %>% 
  full_join(ITG %>% dplyr::select(TOTWGT_Tc3, SENWGT_Tc3, COUNTRY, cycle, questT) %>% 
                    filter(!is.na(TOTWGT_Tc3)) %>% 
                    group_by(COUNTRY, questT) %>% 
                    summarise(n16 = n(),
                              w16 = sum(TOTWGT_Tc3, na.rm = TRUE),
                              w16s =sum(SENWGT_Tc3, na.rm = TRUE)),by = c("COUNTRY", "questT")) %>% 
  arrange(COUNTRY) %>% 
  knitr::kable()
cat('School questionnaires  \n')
cat("\n")
ICG %>% dplyr::select(TOTWGT_Cc1,SENWGT_Cc1, COUNTRY, cycle, questC) %>% 
  filter(!is.na(TOTWGT_Cc1)) %>% 
  group_by(COUNTRY, questC) %>% 
  summarise(n99 = n(),
            w99 = sum(TOTWGT_Cc1, na.rm = TRUE),
            w99s =round(sum(SENWGT_Cc1, na.rm = TRUE),0)) %>% 
  full_join(ICG %>% dplyr::select(TOTWGT_Cc2, SENWGT_Cc2, COUNTRY, cycle, questC) %>% 
                      filter(!is.na(TOTWGT_Cc2)) %>% 
                      group_by(COUNTRY, questC) %>% 
                      summarise(n09 = n(),
                      w09 = sum(TOTWGT_Cc2, na.rm = TRUE),
                      w09s =sum(SENWGT_Cc2, na.rm = TRUE)), by = c("COUNTRY", "questC")) %>% 
              full_join(ICG %>% dplyr::select(TOTWGT_Cc3, SENWGT_Cc3, COUNTRY, cycle, questC) %>% 
                    filter(!is.na(TOTWGT_Cc3)) %>% 
                    group_by(COUNTRY, questC) %>% 
                    summarise(n16 = n(),
                              w16 = sum(TOTWGT_Cc3, na.rm = TRUE),
                              w16s =sum(SENWGT_Cc3, na.rm = TRUE)), by = c("COUNTRY", "questC")) %>% 
  arrange(COUNTRY) %>% 
  knitr::kable()

```

# Description of variables  

```{r descriptive, fig.height = 8, fig.width = 7, results = 'asis', fig.show='asis', eval=FALSE}

source("Data_analysis/Descriptive_Analysis.R")

```


# Confirmatory Factor Analysis (CFA)  

```{r cfa, fig.height = 9, fig.width = 9, results = 'asis', eval=FALSE}

source("Data_analysis/cfa.R")

```

# Multilevel modelling (MLM)  

```{r mlm, fig.height = 9, fig.width = 7, results = 'asis'}

load("Data_analysis/ICCSAll_lv.RData")
source("Data_analysis/mlm.R")
cat('\n')
cat('\n')
cat('## Three level Null model: School nested in countries and in cycles  \n')
t1
cat('\n')
cat('\n')
cat('## Two level Null model: School nested in countries by cycles')
cat('\n')
cat('\n')
t2
t3
t4
cat('\n')
cat('\n')
cat('## Three level model: School nested in countries and in cycles')
cat('\n')
cat('\n')
t5
cat('\n')
cat('\n')
cat('## Two level model: School nested in countries by cycles')
cat('\n')
cat('\n')
b11
b21
b31
```

# Latent Class Analysis  (LCA)

```{r}

library(poLCA)
#LCA1 <- poLCA(, data = ICCS, nclass = 2, graphs = TRUE, na.rm = TRUE)

```


