---
title: "Models using Attitudes toward equality - CIVED 1999/ ICCS 2009/ ICCS 2016"
author: "Pamela Inostroza Fernández"
date: "December 2020"
output: 
  html_document:
    keep_md: true
    toc: TRUE
    toc_depth: 1
    toc_float: 
      collapsed: true
    number_sections: true
    theme: united
    highlight: tango
---

```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = 'C:/Users/pamel/OneDrive - KU Leuven/Master in Statistics/Master Thesis')
library(haven)
library(readxl)
library(tidyverse)
options(scipen = 999)
options(knitr.kable.NA = '')

setwd("C:/Users/pamel/OneDrive - KU Leuven/Master in Statistics/Master Thesis/")
sys.source("Data_analysis/functions.R", envir = knitr::knit_global())

```  


```{r data}
Countries <- read_xlsx("Data_analysis/Metadata.xlsx", sheet = "CNT")
Files <- read_xlsx("Data_analysis/Metadata.xlsx", sheet = "Files")
Scales <- read_xlsx("Data_analysis/Items scales.xlsx", sheet = "Scales")
CNTa <- c("DNK", "FIN", "NOR", "SWE")
CNTb <- c("BFL", "NLD")
CNTc <- c("BGR", "EST", "LVA", "LTU", "HRV", "SVN")
CNTd <- c("ITA", "MLT")
CNTe <- c("CHL", "PER", "COL", "DOM", "MEX")
CNT <- c(CNTa, CNTb, CNTc, CNTd, CNTe)
# c(AUS", "BFL", "BGR", "CHE", "CHL", "COL", "CYP", "CZE", "DEU", "DNK", "DOM", "ENG", "ESP", "EST", "FIN", "FRA", "GRC", "HKG", "HRV", "HUN", "ISR", "ITA", "KOR", "LTU", "LVA", "MEX", "MLT", "NLD", "NOR", "PER", "POL", "PRT", "ROM", "RUS", "SRB", "SVK", "SVN", "SWE", "TWN", "USA") CNTb #

years <- Countries %>% filter(AlphaCode %in% CNT & !is.na(Part)) %>% dplyr::select(Country, AlphaCode, year) 

```


# Multilevel modelling (MLM)  

In this section a multilevel model was performed to evaluate the variability of the scale considering the nested structure of the data. The first model use the three cycles of CIVED/ICCS as a level, followed by Country level and finally School level.
Next, The analysis is performed to all countries participating in each cycle separately, using country and school level. 
Results are obtained for the models indicated using Null model followed by the model with some explanatory variables at the student level. 

Dependant variables:  

Ethn_Equal: Attitudes toward equal rights for all ethnic or racial groups calculated by CFA (min = 0, max = 100)   
Gend_Equal: Attitudes toward gender equality calculated by CFA  (min = 0, max = 100) 
Immi_Equal: Attitudes toward equal rights for immigrants calculated by CFA (min = 0, max = 100) 

Explanatory variables:  

T_AGE: Age of the student   
T_GENDER: Gender of the student [0 = Boy(ref), 1 = Girl]   
T_RELIG: Student's religious affiliation [0 = No Religion(ref), 1 = Religion]    
T_HOMELIT: Home literacy resources [0 = 0-10 books(ref), 1 = 11-25 books, 2 = 26-100 books, 3 = 101-200 books, 4 = More than 200 books]  
T_HISEI: Highest parental occupational status (min = 0, max = 100)   
T_NISB: National index of socioeconomic background  (min = 0, max = 100)


```{r mlm, fig.height = 9, fig.width = 7, results = 'asis'}

load("Data_analysis/ICCSAll_lv.RData")
source("Data_analysis/mlm.R")
cat('\n')
cat('\n')
cat('## Three level model: School nested in countries and in cycles  \n')
cat('\n')
cat('\n')
cat('### Null model  \n')
t1
cat('\n')
cat('\n')
cat('### Model 1  \n')
cat('\n')
cat('\n')
t5
cat('\n')
cat('\n')
cat('### Model 2  \n')
cat('\n')
cat('\n')
t6
cat('\n')
cat('\n')
cat('## Two level model: School nested in countries by cycles  \n')
cat('\n')
cat('\n')
cat('### Null model  \n')
cat('\n')
cat('\n')
t2
t3
t4
cat('\n')
cat('\n')
cat('### Model 1  \n')
cat('\n')
cat('\n')
b11
b21
b31
cat('\n')
cat('\n')
cat('### Model 2  \n')
cat('\n')
cat('\n')
b12
b22
b32
```

# Latent Class Analysis  (LCA) {.tabset .tabset-fade .tabset-pills}

Under construction...

```{r lca, results = 'asis'}

cat('\n')
cat('\n')
cat('## CIVED 1999')
cat('\n')
cat('\n')
#source("Data_analysis/lca.R")
cat('\n')
cat('\n')
cat('## ICCS 2009')
cat('\n')
cat('\n')

cat('\n')
cat('\n')
cat('## ICCS 2016')
cat('\n')
cat('\n')
```

